Equivalence Hypergraphs: E-Graphs for Monoidal Theories

### 2023-10-25 sections/conclusion.tex
fixed clashed figure
conclusion

Symmetric monoidal theories have received significant attention over recent years: the ZX-calculus can be used to characterize quantum processes, with applications to optimization of quantum circuits [cite] ; similar theories also characterize signal flow diagrams 
\cite{baldan_categorical_2014}, digital circuits 
\cite{ghica_operational_2021}, as well as having application to computational linguistics \cite{wazni_quantum_2022,coecke_lambek_2013}.  In future work, we hope to apply our generalization of e-graphs to optimization problems in these domains (e.g. Figure \ref{fig:applications})

>>>>

Symmetric monoidal theories have received significant attention over recent years: the ZX-calculus can be used to characterize quantum processes, with applications to optimization of quantum circuits \cite{coecke_interacting_2011,ZX} ; similar theories also characterize signal flow diagrams 
\cite{baldan_categorical_2014}, digital circuits 
\cite{ghica_operational_2021}, as well as having application to computational linguistics \cite{wazni_quantum_2022,coecke_lambek_2013}.  In future work, we hope to apply our generalization of e-graphs to optimization problems in these domains (e.g. Figure \ref{fig:applications})

### 2023-10-25 sections/e-graph-translation.tex
Fixesing inaccuracies for combinatorial semantics
conclusion

The (convex) \textit{matching} of one e-hypergraph $L$ (\textit{e.g.}, the left-hand side of a rewrite rule) into another e-hypergraph $G$ was defined in the previous section as a monic morphism $L \to G$ (whose image is additionally convex, \update{consistent}). In other words, it corresponds to finding a subgraph isomorphic to $L$ within $G$ (subject to conditions respecing the hierarchical and conflict structures).

However, in general we will have to explode the e-hypergraph, by applying the structural rules for (horizontal, vertical) congruence first, in order to find such a match. In this section, we define the  e-matching (and subsequent e-rewriting) as the problem of finding matches (and applying rewrites) within an e-hypergraph \textit{without} first inducing duplication of subgraphs. We begin first with definitions, before proceeding to prove them “correct” with respect to the plain notion of matching (rewriting). \update{Example}

>>>>

The (convex) \textit{matching} of one e-hypergraph $L$ (\textit{e.g.}, the left-hand side of a rewrite rule) into another e-hypergraph $G$ was defined in the previous section as a monic morphism $L \to G$ (whose image is additionally convex, \update{consistent}). In other words, it corresponds to finding a subgraph isomorphic to $L$ within $G$ (subject to conditions respecting the hierarchical and conflict structures).

However, in general we will have to explode the e-hypergraph, by applying the structural rules for (horizontal, vertical) congruence first, in order to find such a match. In this section, we define the  e-matching (and subsequent e-rewriting) as the problem of finding matches (and applying rewrites) within an e-hypergraph \textit{without} first inducing duplication of subgraphs. We begin first with definitions, before proceeding to prove them correct with respect to the plain notion of matching (rewriting).
